
\noindent
\emph{Lecture - 14\hfill 10 Oct 24, Thu}

\begin{lemma}
	Let $M \in G.$ Then there exists a product $b$ of upper triangular transvections such that $i$ satisfying $1 \leq i \leq n,$ $b M$ has exactly one row, say the $k_i^\text{th}$ row such that the leading non zero entry is in the $i^\text{th}$ column.
\end{lemma}

\begin{proof}
We shall denote non zero entries using $\square$ and $\ast$ to denote any arbitrary entry.
Let 
$$ M = \begin{pmatrix}
	  \ast & \ast & \ast & \ast &\ast \\
	  \ast & \ast & \ast & \ast &\ast \\
	  \square & \ast & \ast & \ast &\ast \\
	    0  & \ast & \ast & \ast &\ast \\
	    0  & \ast & \ast & \ast &\ast
  \end{pmatrix} .$$
Let the last nonzero entry in the first column be in the $i^\text{th}$ row. So $k_i = 1.$
Note that for distinct $i,j$ with $1 \leq i,j \leq n,$ and $\alpha$ in
$\mathbb{F},$ all but the $i^\text{th}$ row of $X_{i \, j }(\alpha)$ are equal to
the rows of $M,$ and the $i^\text{th}$ row of $X_{i \, j} ( \alpha)$ is the $i^\text{th}$ row of $M$ added to $ \alpha$ times the $j^\text{th}$ row of $M.$
In other words, $X_{i \, j } ( \alpha) M[i, ;] = M[i,;] + \alpha M[j,;]$
To ensure that no other entries in the first column are nonzero, we multiple $M$ on the left by transvections $X_{1\, k_1}(-M_{1\,k_1} M_{k_1\,1}^{-1}),$ $ X_{2\, k_1}-(M_{2\,k_1} M_{k_1\,1}^{-1}), \dotsc$ $ X_{k_1-1\, k_1}(-M_{k_1-1 \,k_1} M_{k_1\,1}^{-1})$ which are all upper triangular.
Having ensured that for $l = 1, 2, dotsc, i-1,$ the $l^\text{th}$ column has exactly one row, namely the $k_l^\text{th}$ row such that the leading non zero entry of the $k_l^\text{th}$ row appears in the $l^\text{th}$ row, we can do the same for $l = i.$ Then we have
$$ B_l M = \begin{pmatrix}
	     0    &   0    &   \ast  &    0    &    0    \\
	     0    & \square&   \ast  &  \ast   &    0    \\
	  \square &   0    &   \ast  &  \ast   &    0    \\
	     0    &   0    & \square &  \ast   &    0    \\
	     0    &   0    &    0    &  \ast   &    0    
     \end{pmatrix} $$
     where the $\square$ denotes the leading non zero entry of some row, let us call it $k_i$ where $i$ is the column in which $\square$ exists. By definition of leading non zero entry, $k_i$ is unique for each $i.$  In this way, $B_1W$ is a matrix with 
\end{proof}


\begin{theorem}[Bruhat Decomposition]
	G = BWB
\end{theorem}
\begin{proof}
	Let $M \in G.$ Define $k_i,$ for $i = 1,2,\dotsc, n$ to be the row in which the leading non zero entry of the $i^\text{th}$ row appears.
	So there exists a product $B$ of upper triangular transvections such that $bM$
\end{proof}


Having proven that $G = BWB = \bigcup_{w \in W} B w B,$ we want to prove that this union is a disjoint union. To do this, we shall analyse the normaliser of $B.$

\begin{lemma}
	If $w_1, w_2$ in $W$ and $b $ in $B,$ such that $w_1 b w_2$ is
	in $B,$ then $w_2 = w_1^{-1}.$
\end{lemma}
\begin{proof}
Let $\sigma_1$ and $\sigma_2$ be the permutations associated with $w_1$ and $w_2,$ respectively. Precisely, we have
$w_1 v_i = v_{\sigma_1(i)}$ for each $i$ in $\{ 1, 2, \dotsc, n\}.$
So, the leading nonzero entry in the $j^\text{th}$ column of $b$ is 
transfered to the $\sigma_2(j)^\text{th}$ column by the action of $w_2$ from the right.
So, the leading non zero entry of the $j^\text{th}$ row appears in the $\sigma_2(j)^\text{th}$ column of $bw_2.$
The action of $w_1$ transfers this entry to the $\sigma_1(j)^\text{th}$ row.
So the leading non zero entry of the $j^\text{th}$ row in 
$w_1 b w_2$ appears in the $\sigma_1(\sigma_2(j))^\text{th}$ column for each $j$ in 
$\{1, 2, \dotsc, n\}.$
As $w_1 b w_2$ is also an upper triangular invertible matrix, we can conclude that $\sigma_1(\sigma_2(j)) = j.$
This shows that $w_1 = w_2^{-1}.$
\end{proof}

\begin{corollary}[G as a disjoint union of double cosets]
	If $w$ and $w'$ are distinct elements of $W,$ then 
	$B w B \cap B w' B = \phi.$ Consequently, $G$ is a disjoint union of the $n!$ cosets $BwB$ over $w $ in the Weyl Subgroup $W.$
\end{corollary}


\begin{corollary}[Unique Representation]
\end{corollary}
\begin{proof}
	Let $M$ be in $G$ and let $w$ be the unique element of $W$ such that $M \in BwB.$ Then $w$ sends $v_i$ to $v_{k_i}$ for each $i$ where
	$k_{i}$  is the unique in $\{1, 2 ,\dotsc, n\}$ such that the leading nonzero entry of the $k_i^\text{th}$ row appears in the $i^\text{th}$ column.
	Then 
\end{proof}
\begin{theorem}[Generating Set of $G$]
	$G$ is generated by the set consisting of all invertible diagonal matrixes and all transvections.
\end{theorem}

\begin{proof}
Using the Bruhat decomposition, we know that $G = BWB.$ So it suffices
to show that the set generates $B$ and $W.$ Using upper triangular transvections $t_1, t_2, \dotsc, t_k$ we can make an upper triangular invertible matrix $b$ diagonal. We have $t_1 t_2 \cdots t_k b = d.$ This gives us $b = t_k^{-1} \cdots t_1^{-1} d.$ 
Let $w$ be the element in $W$ which sends $v_i$ to $v_j,$ $v_j$ to $v_i$ and fixes $v_k$ for all $k \not = i$ or $k,$ can be represented as
$w = d X_{i\,j}(1) X_{j\,i}(-1) X_{i\,j}(1)$
where $d$ is the diagonal element with diagonal element equal to $-1$ in the $j^\text{th}$ row and $1$ in the main diagonal in all other rows.
\end{proof}


\begin{definition}[Complete flag on $V_n(\mathbb{F})$]
	A complete flag on $V_n(\mathbb{F})$ is a sequence of subspaces
	$$0 = V_{\{0\}} \leq V_1 \leq V_2 \cdots \leq V_n = V_n(\mathbb{F}).$$
	If each containment is proper, then dimension of $V_i$ is $i$ for each $i$ in $\{1, 2, \dotsc, n\}.$ We denote this flag by $(v_1, v_2, \dotsc, v_n).$
\end{definition}
Let $V_n(\mathbb{F})$ be the $n$ dimensional vector space over $\mathbb{F}$ with standard basis $v_1, v_2 \dotsc v_n.$
The standard flag on $V_n(\mathbb{F})$ is $(V_0, V_1, \dotsc, V_n),$ where
$V_i = V_{i-1} \oplus \mathbb{F} v_i.$

